Collective excitations in the 2- and 3-dimensional extended Hubbard model

### 2023-11-20 paper/collective_excitations.tex
paper text

\keywords{Hubbard model, collective excitations, superconductivity, charge order, spin order}

@@

The Hubbard model at half-filling has been employed in a plethora of previous studies. 
Early studies proved the existence of eigenstates to the Hubbard Hamiltonian that exhibit off-diagonal long-range order, tantalizing the model's usage for the description of high-temperature superconductivity \cite{yang89}.
Shortly afterward, an exact $SO(4)$ symmetry was discovered, which allows a degeneracy of a superconductivity (SC) and a charge-density wave (CDW) with an attractive on-site interaction \cite{yang90}.
There exists a particle-hole transformation on bipartite lattices, that maps the attractive Hubbard model exactly onto the repulsive one, exhibiting antiferromagnetism (AFM).
The previously mentioned SC and CDW phases map to different spin operators \cite{zitko15,lieb89}.
\newline
Many recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity \cite{Nicoletti14,Casandruc15,patel16,sentef17,Buenemann17}.
Other studies focusing on equilibrium systems investigated phases including various additional interaction with and without doping

>>>>

\keywords{Hubbard model, collective excitations, superconductivity, charge density wave, antiferromagnetism}

@@

The Hubbard model at half-filling has been employed in a plethora of previous studies. 
Early studies proved the existence of eigenstates to the Hubbard Hamiltonian that exhibit off-diagonal long-range order,
tantalizing the model's usage for the description of high-temperature superconductivity \cite{yang89}.
Shortly afterward, an exact $SO(4)$ symmetry was discovered,
which allows a degeneracy of superconductivity (SC) and a charge-density wave (CDW) governed by an attractive on-site interaction \cite{yang90}.
This coexistence can be argued by the existence of a particle-hole transformation on bipartite lattices, 
that maps the attractive Hubbard model exactly onto the repulsive one, exhibiting antiferromagnetism (AFM) \cite{Hirsch85}.
The previously mentioned SC and CDW phases map to different spin operators \cite{zitko15,lieb89}.
\newline
Many recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity 
\cite{Nicoletti14,Krull14,Casandruc15,patel16,sentef17,Buenemann17}.
Other studies, focusing on equilibrium systems, 
investigated the phases and various quantities therein of said model including various additional interactions with and without doping 
\cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.
In this paper, we will restrict ourselves to the half-filled Hubbard model, including an additional intersite interaction, on a square and a simple cubic lattice.
\textcolor{red}{Für den 3D Fall finde ich keine Phasendiagramme des extended Hubbard models, ggf nochmal suchen...}
The 2D case already exhibits a wide range of possible phases, including CDW, AFM as well as $s$- and $d_{x^2 - y^2}$-wave superconductivity
\cite{Micnas88b,Tsuchiura95,Su01,Su04,ha11,Huang13,Jiang22}.
\newline
In this article, we will first employ a mean-field approximation to the interaction terms 
and then use the methodology from the so-called iterated equations of motion approach,
which has already seen success in the handling of interaction quenches \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
Here, on commutes operators from a suitable operator basis with the Hamiltonian and adds the newly occurring terms to it.
Naturally, a truncation is necessary for most practical applications, however, the approximation becomes better the more terms are included within the basis.
The functionality of this method has been compared to the density matrix formalism and has proved to be considerably more accurate \cite{Kalthoff17}.
\newline
